\input{preamble}

\begin{document}

\title{Computer Vision Lab \#1: Pointwise Image Processing} 

\author{Ricardo Fabbri and Others \and Based on EN161 Image
Understanding 2011 course material from Brown University}


Your goal of this first lab is to 

\begin{itemize}
\item Familiarize with the Scilab image
processing toolbox (SIP).
\item Implement pointwise image processing operations such as thresholding,
sampling, quantization, and enhancements
\end{itemize}

The images you will need for the lab can be downloaded from the course
website
http://wiki.nosdigitais.teia.org.br/CV

\section{Introduction to the Scilab Image Processing toolbox (SIP)}

\paragraph{Initial tasks:}
\begin{enumerate}
\item Install Scilab and SIP. You will need Linux or Mac OSX.
\item Go through the SIP demos and make sure you understand the \texttt{imshow, imread,
imwrite}, and the other commands showcased in the demo.
\begin{lstlisting}
exec(SIPDEMO);
\end{lstlisting}
\item Read our paper about the toolbox and type in the commands~\cite{SIP}.
Make things work in the desired way even if they don't, since your version of
SIP and Scilab may be different.
\end{enumerate}

\section{Thresholding}

\subsection{Basics} Using the white blood cell image1 as seen below, threshold it to make any
non-cell area black. To do this, you will need to check each pixel in the image,
and if it is over $\tau_0$ (where $\tau_0$ is the threshold you have chosen) set the pixel’s
intensity to 0, otherwise, set to 1. You will need to play with $\tau_0$ to find its
optimal value. You will probably want to pass it into the function as a
parameter.
\code{Threshold Code}{threshold-code.sci}
\subsection{Bilevel Thresholding}
Using the snowman image 2, perform bilevel thresholding. i.e. set all
pixels with intensity between $\tau_0$ and $\tau_1$ to 255 and set all pixels
less than $\tau_0$ 
to 0 and all pixels greater than $\tau_1$ to 0. The snowman is the region of interest,
you are thresholding for (where bob is, should be all white and the rest should
be black).


\end{document}
